### 2018-06-04 express2018/part2.tex
Sync with part2.htex

In the second half of this paper, we present a formalization of all new concepts and
theorems developed in the first part of this paper. The main purpose
is to convince the readers that, there's no flaw\footnote{Perheps this is the first
  time a frontier development in Concurrency Theory ships with its
  formalization in the same paper.} in those informal proofs. This work is based on a rather
complete formalization of CCS in HOL theorem prover
(HOL4), described in a MSc thesis \cite{Chun:2017} and now lives in
the official examples folder of HOL4 source
code\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL}}.
The work is essentially a porting and extension of the early CCS
formalization by Monica Nesi \cite{Nesi} in HOL88.

We will not repeat all concepts and major theorems of CCS again in its
formalized ways, nor talk about the changes and improvements comparing
with previous CCS work including Nesi's. Instead, we just focus on our
targeting theorems. However, as the unique solution of (rooted)
contraction theorem stood at the end of a chain of results, it's
impossible to describe only their statements and formal proofs without
describing many dependent things first.  On the other side, it's very
hard to convince audience the novelty in a proof
engineering work, especially when there exists multiple formalizations
 in the same area. After all, the whole interactive theorem proving (ITP)
technique is just a translation of definitions and hand-made
proofs from their informal representations to their formal versions.

Unlike complicated large programs (e.g. operating systems) which
usually contain countless of bugs even after years of updates and
bugfixes, a huge prove engineering work can easily claim its
\emph{correctness} without concerning other aspects (performance,
quality of definitions, easiness of reading by human, etc.)
Yet still different formalizations (of the same theory) done by
different persons could be huge different, due to the great
flexibilities on choices making at the design of types, terms and
definitions. It's also quite common to break long original proofs into
small lemmas and reuse them in the proof of other relevant
theorems. For the same theorem, good and bad-killed proof engineers
(suppose they both finished the proof)
may result into very different proof steps of huge size
differences.\footnote{But it's not true that a shorter proof is always
better, and a shorted proof may not be executed faster if it heavily
depends on automatic proof searching tools such as Meson and Metis. On
the other side, longer proof without automatic proof searching can be
easier understood by students who are learning the theory being
formalized. Indeed, we have tried to follow the informal proof steps literally, and only used
automatic proof searching techniques on obvious small proof goals.}
Roughly speaking, there're relative ``good'' and ``bad'' designs and
considerations, but if they all \emph{correctly} formalized the same theory, few people
care about their differences, unless they want to extend existing work
to verify their new developments.

>>>>

In the second half of this paper, we present a formalization of CCS
including the new concepts and theorems proposed in the first half of
this paper. The main purpose is to convince the readers that, there's no flaw\footnote{Perheps this is the first
  time a frontier development in Concurrency Theory ships with its
  formalization in the same paper.} in the informal proofs. The formalization work is based on a formalization of CCS in HOL theorem prover
(HOL4), described in second author's MSc thesis \cite{Chun:2017} and now lives in
the official examples folder of HOL4 source
code\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL}}.
The work is essentially a porting and extension of the early CCS
formalization by Monica Nesi \cite{Nesi} in HOL88.

We will not repeat all definitions and theorems of CCS again by their
formalized versions, nor we talk about the changes and improvements
comparing with previous CCS work by Nesi. Instead, we just focus on our
targeting theorems. However, the unique solution of (rooted)
contraction theorem stood at the end of a chain of and
concepts and results, it's
impossible to describe only the final statements and it formal proofs without
describing all dependent concepts first.  On the other side, it's very
hard to convince audience the novelty in a proof
engineering work, especially when there exists multiple formalizations
 in the same area. After all, the whole interactive theorem proving (ITP)
technique is just a translation of definitions and hand-made
proofs from their informal representations to their formal versions.

Unlike complicated large programs (e.g. operating systems) which
usually contain countless of bugs even after years of updates, a huge
proof engineering work can easily claim its
\emph{correctness} without concerning other aspects (performance,
quality of definitions, easiness of reading by human, etc.)
Yet still different formalizations (of the same theory) done by
different persons could be very different, due to the great
flexibilities on choices made during the design of types, terms and
definitions. It's also quite common to break the original long proofs to
small pieces. For the same theorem, good and bad-killed proof engineers
may result into very different proof steps with quite different
lenths.\footnote{But it's not true that a shorter proof is always
better, and a shorted proof may not be executed faster if it heavily
depends on automatic proof searching tools such as Meson and Metis. On
the other side, longer proof without automatic proof searching can be
easier understood by students who are learning the theory being
formalized. Indeed, we have tried to follow the informal proof steps literally, and only used
automatic proof searching techniques on obvious small proof goals.}
Roughly speaking, there're relative ``good'' and ``bad'' designs and
considerations, but if they all \emph{correctly} formalized the same theory, few people
care about their differences, unless they want to extend existing work
to verify their new developments.
